The Space of Feasible Execution Times for Asynchronous Periodic Task Systems using Definitive Idle Times

### 2013-09-18 dit-paper_ieee.tex
rewritten FPDIT existence and construction

		As in the synchronous case, the problem of existence of the FPDIT
		can be written as a system of modular equations:
		\begin{equation}
			\begin{array}{l}
				\exists ? \; t_d \; s.t. \; \forall \tau_i \in \tau, \exists a_i \in [D_i,
				T_i] \; :\\
				\left\{
					\begin{array}{l}
						t_d > O_i \\
						t_d - O_i \equiv a_i \; (mod \;	T_i)
						\\
					\end{array}
				\right.
			\end{array}
		\end{equation}
		This system is equivalent to an instance of the Chinese Remainder Problem
		(CRP) where the goal is to find the value of $t_d$ such that it is congruent
		to $a_i+O_i$ modulo $T_i$ for all tasks $\tau_i$ in $\tau$. We define $x_i =
		a_i+O_i$ and $n_i = T_i$ for clarity in the context of the CRP. This problem
		is guaranteed to have at least one solution modulo $H$ for given values of
		$a_i$ if Condition~\ref{eq:CRPcond} is respected
		\cite{knuth1969art}:
		\begin{equation}
			\label{eq:CRPcond}
			x_i \equiv x_j \; (\operatorname{mod} \; \operatorname{gcd}(n_i, n_j))
			\; \forall \tau_i,\tau_j \in \tau
		\end{equation}
		Condition~\ref{eq:CRPcond} means that DITs might still exist even though in
		the general case task periods will not necessarily be pairwise coprime.
% 		We now present an example of such a system.\\
% 
% 		\begin{center}
% 			\begin{tabular}{|r|c|c|c|c|}
% 				\hline
% 							& $O_i$ & $C_i$ & $D_i$ & $T_i$ \\ \hline
% 				$\tau_1$ 	& 0 	& $C_1$ & 3 	& 4\\ \hline
% 				$\tau_2$ 	& 2 	& $C_2$ & 7 	& 8\\ \hline
% 			\end{tabular}
% 		\end{center}
% 
% 		Here, the possible values of $a_1$ are 3 and 4, and the possible values
% 		of $a_2$ are 7 and 8. For a FPDIT to exist, one of the following
% 		conditions must be fulfilled:
% 		\[
% 			\left[
% 			\begin{array}{c}
% 				3 + 0 \equiv 7 + 2 \; (\operatorname{mod} \; 4 ) \\
% 				3 + 0 \equiv 8 + 2 \; (\operatorname{mod} \; 4 ) \\
% 				4 + 0 \equiv 7 + 2 \; (\operatorname{mod} \; 4 ) \\
% 				4 + 0 \equiv 8 + 2 \; (\operatorname{mod} \; 4 ) \\
% 			\end{array}
% 			\right.
% 		\]
% 		However neither is, which means the system has
% 		no FPDIT (and no other DIT than $t=0$).

@@

				\FORALL{$\tau_i \in \tau$}
					\STATE $Mj \leftarrow \frac{H}{n_i}$
					\STATE $invMj \leftarrow Mj^{-1} \; (mod \; n_i)$
					\STATE $e_i \leftarrow Mj \cdot invMj$
				\ENDFOR
				\RETURN $\sum\limits_{\tau_i \in \tau}{x_i \cdot e_i} \; (mod \; H)$
			\end{algorithmic}
		\end{algorithm}
		Algorithm~\ref{alg:algoCRP} finds one DIT given one value of $a_i$ per task.
		However using it in practice is very inefficient as there are
		exponentially many different combinations of $a_i$ values in the number of
		tasks, and resolving exponentially many CRP instances is prohibitively slow.
		A faster method for finding the FPDIT consists in merging all these CRP
		instances into one problem (finding all DITs), which can be solved faster by
		Algorithm~\ref{alg:multiACRP}, as a significant part of the intermediate
		results are shared between instances.

@@

				\STATE Modify the $n_i$ and the content of the $X_i$ by prime
				\\ decomposition so that the $n_i$ become pairwise coprime

@@

		Both Algorithm~\ref{alg:algoCRP} and Algorithm~\ref{alg:multiACRP} require the
		computation of one modular inversion per $a_i$ value, which is done in linear
		time with the number of tasks. However, to find all DITs
		Algorithm~\ref{alg:algoCRP} has to be executed once for each possible
		combination of $a_i$ values, which is exponential in the number of tasks.
		Algorithm~\ref{alg:multiACRP} has the same theoretical complexity as the computation of all DITs still requires an exponential number
		of answers in the number of tasks, but it is nonetheless significantly faster
		in practice. The running time of Algorithm~\ref{alg:multiACRP} is also less
		sensitive to the number of different $a_i$ values per task, which means tasks
		with deadlines significantly smaller than periods remain practical.

>>>>

		As in the synchronous case, the problem of existence of the FPDIT
		can be written as a system of modular equations:
		\begin{equation}
			\begin{array}{l}
				\exists ? \; t_d \; s.t. \; \forall \tau_i \in \tau, \exists a_i \in [D_i,
				T_i] \; :\\
				\left\{
					\begin{array}{l}
						t_d > O_i \\
						t_d - O_i \equiv a_i \; (mod \;	T_i)
						\\
					\end{array}
				\right.
			\end{array}
		\end{equation}

		This system is equivalent to multiple instances (one per combination of $a_i$
		values) of the Chinese Remainder Problem (CRP) where the goal is to find the
		value of $t_d$ such that it is congruent to $a_i+O_i$ modulo $T_i$ for all
		tasks $\tau_i$ in $\tau$. To find the FPDIT it is to the best of our knowledge
		necessary to solve the problem on all combinations of $a_i$ values then
		compute the minimum solution. We define $x_i = a_i+O_i$ and $n_i = T_i$ for
		clarity in the context of the CRP. One instance of this problem is guaranteed
		to have at least one solution modulo $H$ for given values of $a_i$ if
		Condition~\ref{eq:CRPcond} is satisfied \cite{knuth1969art}:
		\begin{equation}
			\label{eq:CRPcond}
			x_i \equiv x_j \; (\operatorname{mod} \; \operatorname{gcd}(n_i, n_j))
			\; \forall \tau_i,\tau_j \in \tau
		\end{equation}
		Condition~\ref{eq:CRPcond} means that DITs might still exist even though in
		the general case task periods will not necessarily be pairwise coprime.
% 		We now present an example of such a system.\\
% 
% 		\begin{center}
% 			\begin{tabular}{|r|c|c|c|c|}
% 				\hline
% 							& $O_i$ & $C_i$ & $D_i$ & $T_i$ \\ \hline
% 				$\tau_1$ 	& 0 	& $C_1$ & 3 	& 4\\ \hline
% 				$\tau_2$ 	& 2 	& $C_2$ & 7 	& 8\\ \hline
% 			\end{tabular}
% 		\end{center}
% 
% 		Here, the possible values of $a_1$ are 3 and 4, and the possible values
% 		of $a_2$ are 7 and 8. For a FPDIT to exist, one of the following
% 		conditions must be fulfilled:
% 		\[
% 			\left[
% 			\begin{array}{c}
% 				3 + 0 \equiv 7 + 2 \; (\operatorname{mod} \; 4 ) \\
% 				3 + 0 \equiv 8 + 2 \; (\operatorname{mod} \; 4 ) \\
% 				4 + 0 \equiv 7 + 2 \; (\operatorname{mod} \; 4 ) \\
% 				4 + 0 \equiv 8 + 2 \; (\operatorname{mod} \; 4 ) \\
% 			\end{array}
% 			\right.
% 		\]
% 		However neither is, which means the system has
% 		no FPDIT (and no other DIT than $t=0$).

@@

				\FORALL{$\tau_i \in \tau$}
					\STATE $Mj \leftarrow \frac{H}{n_i}$
					\STATE $invMj \leftarrow Mj^{-1} \; (mod \; n_i)$
					\STATE $e_i \leftarrow Mj \cdot invMj$
				\ENDFOR
				\RETURN $\sum\limits_{\tau_i \in \tau}{x_i \cdot e_i} \; (mod \; H)$
			\end{algorithmic}
		\end{algorithm}
		Algorithm~\ref{alg:algoCRP} finds one DIT given one combination of $a_i$
		values. However using it in practice is very inefficient as there are
		exponentially many different combinations of $a_i$ values in the number of
		tasks, and resolving exponentially many CRP instances is prohibitively slow.
		A faster method for finding the FPDIT consists in merging all these CRP
		instances into one problem (finding all DITs), which can be solved faster by
		Algorithm~\ref{alg:multiACRP}, as a significant part of the intermediate
		results are shared between instances.

@@

				\STATE Modify $n_i$ and the content of $X_i$ by prime
				\\ decomposition to get pairwise coprime $n_i$ values

@@

		Both Algorithm~\ref{alg:algoCRP} and Algorithm~\ref{alg:multiACRP} require the
		computation of one modular inversion per $a_i$ value, which is done in a
		linear number of modular inversions per task. However, to
		find all DITs Algorithm~\ref{alg:algoCRP} has to be executed once for each possible
		combination of $a_i$ values, which is exponential in the number of tasks.
		Algorithm~\ref{alg:multiACRP} has the same theoretical complexity as the
		computation of all DITs still requires an exponential number of answers in the
		number of tasks, but it is nonetheless significantly faster in practice. The
		running time of Algorithm~\ref{alg:multiACRP} is also less sensitive to the
		number of different $a_i$ values per task, which means that this method
		remains practical when tasks deadlines are much smaller than periods.
